Pursuit of Happiness: The impact of authoritarian government policies on Chinese well-being

### 2024-04-23 paper/paper.qmd
please

While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the recent developments in China. This study will extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China in the past few years and their implications for SWB. We analyze whether the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.

In this project, the estimand will be the difference in happiness level between each participant based on information like national pride, government support, and age.

@@

To continue our paper based on Steele and Lynch, we obtained our data from the World Values Survey. The World Values Survey is the largest non-commercial international investigation of human values ever executed. There are no other datasets of a similar size that target human beliefs and opinions. While Steele and Lynch used time series data from three surveys (1990, 2001, 2007), we aim to look at more recent trends so we will include the World Values Survey data obtained from their 2018 wave. To be included into the survey dataset, countries must meet a minimum of 1200 entries. Since the survey is global, general guidelines are provided to the teams that are responsible for each country, but slight alterations in sampling method were permitted. The most common method of data collection consisted of face-to-face interviews with respondents at their home, and the answers were recorded on a paper questionnaire for later processing. For China, participants were chosen through probability sampling. The initial dataset contained 94278 responses and 606 variables, but after filtering for responses from China and removing non-responses, we are left with 3036 observations. Each wave of the survey is slightly different, so the wording of some questions and answers may vary. Although the sample for China was chosen through random sampling, survey guidelines dictated that there would be no replacement for non-responses. Therefore, missing data had to be parsed out.

>>>>

While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the recent developments in China. This study will extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China in the past few years and their implications for SWB. Specifically, we will analyze whether there is a relationship between these cultural orientations and well-being.

Our findings indicate that citizens' support for authoritarian policies does not significantly affect their overall happiness. Conversely, national pride appears to have a much more substantial influence on happiness, suggesting that support for CCP policies may not be directly tied to nationalism.

In this project, the estimand will be the difference in happiness level between each participant based on information like national pride, government support, and age. Given the increasing Western discontent with China, these findings could help mitigate xenophobia by highlighting the distinction between the Chinese government and its citizens.

@@

To continue our paper based on Steele and Lynch, we obtained our data from the World Values Survey. The World Values Survey is the largest non-commercial international investigation of human values ever executed. There are no other datasets of a similar size that target human beliefs and opinions. While Steele and Lynch used time series data from three surveys (1990, 2001, 2007), we aim to look at more recent trends so we will use the World Values Survey data obtained from their 2018 wave. To be included into the survey dataset, countries must meet a minimum of 1200 entries. Since the survey is global, general guidelines are provided to the teams that are responsible for each country, but slight alterations in sampling method were permitted. The most common method of data collection consisted of face-to-face interviews with respondents at their home, and the answers were recorded on a paper questionnaire for later processing. For China, participants were chosen through probability sampling. The initial dataset contained 94278 responses and 606 variables, but after filtering for responses from China and removing non-responses, we are left with 3036 observations. Each wave of the survey is slightly different, so the wording of some questions and answers may vary. Although the sample for China was chosen through random sampling, survey guidelines dictated that there would be no replacement for non-responses. Therefore, missing data had to be parsed out.
